NFC and burnout in teachers - A replication and extension study

### 2022-07-21 Manuscript/Manuscript.Rmd
changed section counter

keywords          : "behaviour, resources, demands, education, Covid-19"
wordcount         : "~ 5600"
bibliography      : NFC_Burnout.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : sage-harvard.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{chngcntr}
---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\counterwithout{table}{section}
\setcounter{figure}{0}
\setcounter{table}{0}

@@

# Supplementary Material

## S1: Items used to assess Covid burden

@@

\newpage
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{0}

## S2: Results when excluding the outlier with very high MBI scores and very low NFC scores

@@

## S3: Replication of Grass et al. (2018) when including years spent teaching

@@

## S4: Demand-resource-ratio model with the MBI subscale reduced personal efficacy

@@

## S5: Exploratory model with all relevant variables

>>>>

keywords          : "behaviour, resources, demands, education, Covid-19"
wordcount         : "~ 5600"
bibliography      : NFC_Burnout.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : sage-harvard.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{chngcntr}
---
\renewcommand\thesection{\Alph{section}}
\renewcommand\thesubsection{\arabic{subsection}}
\counterwithout{figure}{section}
\counterwithout{table}{section}
\setcounter{figure}{0}
\setcounter{table}{0}

@@

\newpage
\setcounter{section}{19}
\counterwithin{subsection}{section}
\setcounter{subsection}{0}
\counterwithin{figure}{subsection}
\counterwithin{table}{subsection}
\setcounter{figure}{0}
\setcounter{table}{0}

\section{Supplementary Material}
\subsection{Items used to assess Covid burden}

@@

\subsection{Results when excluding the outlier with very high MBI scores and very low NFC scores}

@@

\subsection{Replication of Grass et al. (2018) when including years spent teaching}

@@

\subsection{Demand-resource-ratio model with the MBI subscale reduced personal efficacy}

@@

\subsection{Exploratory model with all relevant variables}
